Anonymous provision of services via blockchain

### 2022-03-04 access.tex
update abstract

\begin{abstract}
Service providers like lawyers, laboratories, auditors, or banks, to
provide services, require customers to submit data often
associated with their personal information. This situation exposes
customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments
and communication and could provide services anonymously if other means of logistics exist.

We propose a protocol for coordinating local anonymous service
provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.

A service provider can employ our protocol to provide
services without collecting any personal information. Possible
applications for this protocol include anonymous clinical drug testing,
steroid, parenting testing, anonymous legal advice, or
anonymous financial trustworthiness evaluation.

In case of dispute, either due to exceeding deadlines or providing
incorrect result, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehavior of the service
provider.

We analyze the protocol in the context of fairness and discuss further
extensions to an anonymous delivery system, payment with cash, and
decentralized conflict resolution system.

Our protocol can enable various services currently based on unacceptable trust assumptions to the SP.
%JS to framework czy protocol?
%SB zmieniłem na protocol, framework jest zbyt abstrakcyjne
\end{abstract}

@@

%JS moze\section{Building Blocks}
%SB Dla mnie idealnie.
\section{Building Blocks}\label{sec:building-blocks}
%JS bacground czego?  
%SB To jest takie wprowadzenie i opisanie wszystkich elementów które będą potrzebne do stowrzenia protokołu. Czy Preliminaries będzie ok?
\subsection{Dispute resolution system}

@@

The second approach is more philosophical and visionary. Suppose that the service we are undertaking is fully computable. Then, it would be possible by employing proofs of correctness of computations~\cite{ben2013snarks} to enforce that only correct computations (hence correct services) are accepted. To do so the whole service examination would have to be computable, which is hard to achieve in settings where physical materials (like blood) are examined. Concretely, the problem canes down to ``How to digitally represent blood''. If we could represent urine, blood, saliva, or any other physical material in binary format, and let the customer take a sample, discrete it, and send it to the SP by himself, then the whole chain of integrity could be ensured. Therefore, wrong service provision would be infeasible.

@@

Without loss of generality, the payment can be made with cash. The customer can exchange the cash with SP together with delivering the package. The $\mathrm{PoD}$ would contain information that the transaction has been paid with cash; therefore, Steps 1 and 2 could be merged and realized in one step. In case of dispute, the payment disclosure would be included in $\mathrm{PoD}$.

>>>>

\begin{abstract}
Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information. This situation exposes customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
We propose a protocol for coordinating anonymous service provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.
A service provider can employ our protocol to provide services without collecting personal information. Possible applications for this protocol include anonymous clinical drugs, steroids, parenting testing, or anonymous legal advice.
In case of dispute, either due to exceeding deadlines or providing incorrect results, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the service provider.
We analyze the protocol in the context of fairness and discuss further extensions to an anonymous delivery system, payment with cash, and a decentralized conflict resolution system.
Our protocol may enable various services currently based on unacceptable trust assumptions to the SP.
\end{abstract}

@@

%JS moze\section{Building Blocks}
%SB Dla mnie idealnie.
\section{Building Blocks}\label{sec:building-blocks}

\subsection{Dispute resolution system}

@@

The second approach is more philosophical and visionary. Suppose that the service we are undertaking is fully computable. Then, it would be possible by employing proofs of correctness of computations~\cite{ben2013snarks} to enforce that only correct computations (hence correct services) are accepted. To do so the whole service examination would have to be computable, which is hard to achieve in settings where physical materials (like blood) are examined. Concretely, the problem canes down to ``How to digitally represent blood?''. If we could represent urine, blood, saliva, or any other physical material in binary format, and let the customer take a sample, discrete it, and send it to the SP by himself, then the whole chain of integrity could be ensured. Therefore, wrong service provision would be infeasible.

@@

Without loss of generality, the payment can be made with cash. The customer can exchange the cash with SP together with delivering the package. The $\mathrm{PoD}$ would contain information that the transaction has been paid with cash; therefore, steps one and two could be merged and realized in one step. In case of dispute, the payment disclosure would be included in $\mathrm{PoD}$.
